---
title: "FRED"
author: "Linh Bun"
date: '2017-09-20'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
output: 
  html_document:
    toc: TRUE
abstract: This is an abstract for R Markdown on getting and accessing publicly available data from the Saint Louis Fed (FRED) database. It is one of an important macroeconomic dataset available publicly at free of charge.
---

# R Markdown Setup
`keep_md: TRUE` option is for keeping Markdown document used to generate HTML but Markdown is rendered better on GitHub. `number_sections: TRUE` option is used to number sections.


# Accessing FRED Data
So far, there seems to be several useful (although there are many more packages for working with St. Louis Fed FRED data):

* `tidyquant`
* `quantmod`
* `alfred`

## `tidyquant` package
We could use `tidyquant::tq_get()` and for St. Louis Fed (FRED database), `tidyquant` uses a wrapper for `quantmod` package. The code for **homeowner vacancy rate (quarterly)** on FRED database is `"RHVRUSQ156N"`.
```{r}
suppressMessages(library("tidyquant"))
# FRED code for Homeowner Vacancy Rate for the US: "RHVRUSQ156N"
homeowner_vacancy_rate <- "RHVRUSQ156N"
housing <- tq_get(homeowner_vacancy_rate, get = "economic.data")
housing
```
```{r}
housing
```
```{r sum1}
str(housing)
```

```{r}
head(housing)
tail(housing)
```


### specifying date range
```{r fred2}
housing2 <- tq_get(homeowner_vacancy_rate,
                   get = "economic.data",
                   # from = "1956-01-01",
                   from = "2001-01-01",
                   to = "2017-06-01")
```


```{r sum2}
str(housing2)
```

```{r}
head(housing2)
tail(housing2)
```

### plots
```{r load_ggplot}
suppressMessages(library("ggplot2"))
```

```{r tq_plot, dpi=300}
ggplot(data = housing,
       mapping = aes(x = date, y = price)) +
    geom_line(color = "blue", size = 1)
```

#### add `scale` package
`scale` package is added for `scale_x_date` labels.
```{r scale_pack}
suppressMessages(library("scales"))
suppressMessages(library("ggbeeswarm"))
suppressMessages(library("hrbrthemes"))
suppressMessages(library("tidyverse"))
```


```{r homeowner_plot, dpi=300}
ggplot(data = housing2) +
    geom_line(mapping = aes(x = date, y = price), 
              color = "blue",
              size = 0.6) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Percent",
         title = "Homeowner Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_ipsum_rc(grid = "XY")
```

```{r homeowner_plot2, dpi=300}
ggplot(data = housing2) +
    # y ==> devide by 100
      # scales::percent ==> multiple things by 100
    geom_line(mapping = aes(x = date, y = price/100), 
              color = "blue",
              size = 0.6) +
    # scale_y_continuous(labels = percent) +
    scale_y_continuous(labels = scales::percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Homeowner Vacancy Rate",
         title = "Homeowner Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_ipsum_rc(grid = "XY")
```

```{r homeowner_plot_dark, dpi=300}
ggplot(data = housing2) +
    geom_line(mapping = aes(x = date, y = price), 
              color = "red",
              size = 0.7) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Percent",
         title = "Homeowner Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_modern_rc(grid = "XY")

```

```{r homeowner_plot_dark2, dpi=300}
ggplot(data = housing2) +
    # y ==> devide by 100
      # scales::percent ==> multiple things by 100
    geom_line(mapping = aes(x = date, y = price/100), 
              color = "red",
              size = 0.7) +
    # scale_y_continuous(labels = percent) +
    scale_y_continuous(labels = scales::percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Homeowner Vacancy Rate",
         title = "Homeowner Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_modern_rc(grid = "XY")

```

```{r tq_plot2_old, dpi=300, echo=FALSE, include=FALSE}
homeowner_vac_plot <- ggplot(data = housing, mapping = aes(x = date, y = price))
homeowner_vac_plot <- homeowner_vac_plot +
    geom_line()
print(homeowner_vac_plot)
```


### Rental Vacancy Rates
The code for **rental vacancy rates** on FRED database is `"RRVRUSQ156N"`.

```{r rental_vac_rate}
rental_vacancy_rate <- tq_get("RRVRUSQ156N",
                              get = "economic.data",
                              from = "2001-01-01",
                              to = "2017-06-01")
```

```{r rental_ht}
head(rental_vacancy_rate)
tail(rental_vacancy_rate)
```

```{r rental_all}
rental_vacancy_rate
```

```{r rental_sum}
str(rental_vacancy_rate)
```

### Plot

```{r rental_plot, dpi=300}
ggplot(data = rental_vacancy_rate) +
    geom_line(mapping = aes(x = date, y = price), 
              color = "blue",
              size = 0.6) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Percent",
         title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_ipsum_rc(grid = "XY")
```

```{r rental_plot2, dpi=300}
ggplot(data = rental_vacancy_rate) +
     # y ==> devide by 100
        # scales::percent ==> multiple things by 100
     geom_line(mapping = aes(x = date, y = price/100), 
              color = "blue",
              size = 0.6) +
    # scale_y_continuous(labels = percent) +
    scale_y_continuous(labels = scales::percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Rental Vacancy Rate",
         title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_ipsum_rc(grid = "XY")
```

```{r rental_plot_dark, dpi=300}
ggplot(data = rental_vacancy_rate) +
    geom_line(mapping = aes(x = date, y = price), 
              color = "red",
              size = 0.7) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Percent",
         title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_modern_rc(grid = "XY")
```

```{r rental_plot_dark2, dpi=300}
ggplot(data = rental_vacancy_rate) +
    # y ==> devide by 100
      # scales::percent ==> multiple things by 100
    geom_line(mapping = aes(x = date, y = price/100), 
              color = "red",
              size = 0.7) +
    # scale_y_continuous(labels = percent) +
    scale_y_continuous(labels = scales::percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Rental Vacancy Rate",
         title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_modern_rc(grid = "XY")
```

### All Data
```{r all_data}
vacancy_rate <- tq_get(c("RHVRUSQ156N", "RRVRUSQ156N"),
                       get = "economic.data",
                       from = "2001-01-01",
                       to = "2017-06-01")
```

```{r all_data_sum}
str(vacancy_rate)
```

```{r all_data_ht}
head(vacancy_rate)
tail(vacancy_rate)
```

```{r}
vacancy_rate
```

### Plot
```{r all_data_plot, dpi=300}
ggplot(data = vacancy_rate) +
    geom_line(mapping = aes(x = date, y = price),
              color = "blue",
              size = 0.6) +
    facet_wrap(~ symbol,
               scales = "free_y",
               nrow = 2) +
    # scale_y_continuous(labels = scales::percent) +
    scale_y_continuous(labels = percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Vacancy Rates",
         # title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_ipsum_rc(grid = "XY")
```

```{r all_data_plot2, dpi=300}
ggplot(data = vacancy_rate) +
    # y ==> devide by 100
      # scales::percent ==> multiple things by 100
    geom_line(mapping = aes(x = date, y = price/100),
              color = "blue",
              size = 0.6) +
    facet_wrap(~ symbol,
               scales = "free_y",
               nrow = 2) +
    # scale_y_continuous(labels = percent) +
    scale_y_continuous(labels = scales::percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Vacancy Rates",
         # title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_ipsum_rc(grid = "XY")
```

```{r all_data_plot_dark, dpi=300}
ggplot(data = vacancy_rate) +
    geom_line(mapping = aes(x = date, y = price),
              color = "red",
              size = 0.7) +
    facet_wrap(~ symbol,
               scales = "free_y",
               nrow = 2) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Percent",
         # title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_modern_rc(grid = "XY")
```

```{r all_data_plot_dark2, dpi=300}
ggplot(data = vacancy_rate) +
    # y ==> devide by 100
      # scales::percent ==> multiple things by 100
    geom_line(mapping = aes(x = date, y = price/100),
              color = "red",
              size = 0.7) +
    facet_wrap(~ symbol,
               scales = "free_y",
               nrow = 2) +
    scale_y_continuous(labels = scales::percent) +
    # scale_y_continuous(labels = percent) +
    # adjusting date break and showing ONLY years
    scale_x_date(date_breaks = "2 years",
                 labels = date_format("%Y")) +
    # rotate years on x axis to avoid overlapping
    theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
    labs(x = "Year",
         y = "Vacancy Rates",
         # title = "Rental Vacancy Rate (Quarterly)",
         # caption = "U.S. Census Bureau: Housing Vacancy Survey. Retrieved from Saint Louis Federal Reserve Bank FRED database using tidyquant package.") +
         caption = "U.S. Census Bureau: Housing Vacancy Survey (St. Louis Federal Reserve Bank: FRED).") +
    theme_modern_rc(grid = "XY")
```


## `quantmod` package